Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-11-30 rCode/Draft.Rmd
tiny tweaks

### Extension Relative to Baccini and Weymoth (2021)

@@

If we expand our measure of net manufacturing job losses to include the 2004 to 2011 period - which covers most of the period when the U.S. manufacturing economy was hit most intensely (See Figure 1) -- we get a result that corroborates the core intuition of Baccini and Weymouth (See Table 4). That is, we find that net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased democratic vote share.

@@

[Note: to demonstrate our point about **variable** effects, In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in democratic vote share in other elections (2012 and 2020).]

@@

We find that, in aggregate, manufacturing job losses were a driver of change in Democratic vote share in the 2016 election. Breaking it down by race, we see that [TO DO: complete thought]. Using our main results from regression 3 in Table 4, we simulate a counterfactual scenario to demonstrate the practical signifcance of our estimates. Specifically, we generate a counterfactual democratic vote share assuming that all counties experienced manufacturing job losses equivalent to the county at the 25th national percentile. In Figure 3, we show the difference between the counterfactual democratic vote share and the model-predicted democratic vote share. We highlight states in purple if the difference between the counterfactual and model-predicted democratic vote shares exceeded Trump's vote share margin. Figure 3 shows that the effect sizes from our analysis suggest that, but for manufacturing layoffs from 2004-2015, Trump may not have one the 2016 presidential election.

@@

We find that, in aggregate, manufacturing job losses were associated with loss of Democratic vote share in the 2016 election. 10 manufacturing job losses per worker in a county since 2004 corresponded to a 3.8 \% loss in vote share, plus or minus 3.3 \%. Breaking it down by race, we see that white

>>>>

### Extension Relative to Baccini and Weymouth (2021)

@@

If we expand our measure of net manufacturing job losses to include the 2004 to 2011 period - which covers most of the period when the U.S. manufacturing economy was hit most intensely (See Figure 1) -- we get a result that corroborates the core intuition of Baccini and Weymouth (See Table 4). That is, we find that net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased Democratic vote share.

@@

[Note: to demonstrate our point about **variable** effects, In our next iteration of the analysis, we will show that manufacturing job losses had little explanatory effect on changes in Democratic vote share in other elections (2012 and 2020).]

@@

We find that, in aggregate, manufacturing job losses were associated with loss of Democratic vote share in the 2016 election. 10 manufacturing job losses per worker in a county since 2004 corresponded to a 3.8 \% loss in vote share, plus or minus 3.3 \%. Breaking it down by race, we see that [TO DO: complete thought].

Figure 3 demonstrates the practical significance of our estimates. Using our main results from regression 3 in Table 4, we simulate a counterfactual 2016 election assuming that all counties experienced white manufacturing job losses equivalent to the county at the 25th national percentile. We highlight states in purple if this counterfactual shows a state flipping from Trump to Clinton.

@@
